Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2023-12-19 paper.tex
Change documentclass to revtex4-1

\documentclass[1p]{elsarticle}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage[export]{adjustbox}

@@

\bibliographystyle{elsarticle-num}
\journal{Physica A: Statistical Mechanics and its Applications}

\begin{document}

\author[Smith]{Vasily~Postnicov}
\author[Smith]{Marina~V.~Karsanina}
\author[Smith,MIT]{Aleksey~Khlyupin}
\author[Smith]{Kirill~M.~Gerke\corref{maincorr}}
\cortext[maincorr]{Corresponding author}
\ead{kg@ifz.ru}

\address[Smith]{Schmidt Institute of Physics of the Earth of Russian Academy of
  Sciences, Moscow, 107031, Russia}
\address[MIT]{Moscow Institute of Physics and Technology,
  Dolgoprudny, 141701, Russia}

@@

\begin{keyword}
  Arrays, multiplication, addition
\end{keyword}

@@

There are two common boundary conditions when applying $\mathfrak{S}$. The
first condition is to extend $A_n$ periodically (\cref{fig:s3-periodic}) when
accessing out-of-bounds array elements. In this case $\mathfrak{S}_z$ is a
circular shift operator:
\begin{equation}
  A[x] \leftarrow A[x+z \mod d]
\end{equation}
In this case $Norm(A, x_1, x_2)$ does not depend on $x_1$ and $x_2$ and
is equal to the total number of elements in $A$. The second condition is to
replace out-of-bound elements with zeros (so-called zero padding)
(\cref{fig:s3-zeros}). A formula for $Norm(A, x_1, x_2)$ in this case is in
\ref{sec:number-of-trials} and $\mathfrak{S}_z$ is defined as follows:
\begin{equation}
  A[x] \leftarrow \left\{
  \begin{array}{ll}
    A[x+z] & \quad \text{if $x+z$ is a correct index in $A$} \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation}
\begin{figure*}[tp]
  \centering
  \subfigure[Periodic boundary conditions]{
    \includegraphics[width=0.45\linewidth]{images/periodic.png}
    \label{fig:s3-periodic}}
  \hfill
  \subfigure[Zero padding]{
    \includegraphics[width=0.45\linewidth]{images/zeros.png}
    \label{fig:s3-zeros}}
  \caption[]{Computation of unnormalized $S_3$ function at point $(1, 2)$ for
    one-dimensional sequence of length 8.}
  \label{fig:s3-computation}
\end{figure*}

@@

On \cref{fig:balls} there is an intersection of such a set with $R = 0.02$ and
$\lambda=5000$ and a cube $[0, 1]^3$. Because $R \ll 1$, we can use
\cref{eq:s2-balls} to verify our computations -- this is exactly what we present on
\cref{fig:balls-s3-comparison}.
\begin{figure*}[tp]
  \centering
  \subfigure[Realization of overlapping balls]{
    \includegraphics[width=0.45\linewidth]{images/balls.png}
    \label{fig:balls}}
  \hfill
  \subfigure[A plot of $S_3(0, r)$ computed with our algorithm and theoretical
    formula.]{
    \includegraphics[width=0.45\linewidth]{images/balls-s3.png}
    \label{fig:balls-s3-comparison}}
  \caption[]{A comparison of calculated and theoretical values of $S_3$ function
    for overlapping balls.}
  \label{fig:s3-verification}
\end{figure*}

@@

The test is performed by firstly evaluating the inequation in a cube
$[-1, 1]^3$ and obtaining precise values of $F_{sss}$ and secondly computing
$F_{sss}$ with our algorithm, giving a discretized $400 \times 400 \times 400$
pixels wide image as the input. $F_{sss}$ function is evaluated in $XY$
plane. Pointwise relative error of $F_{sss}$ is on
\cref{fig:sss-dumbbell-error}. Maximal relative error in the area distanced
farther than 0.1 (20 pixels) from curves of discontinuity (see
\cref{fig:sss-dumbbell-precise}) is no more than 20\%.
\begin{figure*}[tp]
  \centering
  \subfigure[The dumbbell-like object used in testing of $F_{sss}$ computation]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell.png}
    \label{fig:sss-dumbbell}}
  \hfill
  \subfigure[Relative error of computation]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-err.png}
    \label{fig:sss-dumbbell-error}}
  \vskip\baselineskip
  \subfigure[$F_{sss}$: precise. The correlation function is undefined (has type
    II discontinuity) at curves A, B and C.]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-precise.png}
    \label{fig:sss-dumbbell-precise}}
  \hfill
  \subfigure[$F_{sss}$: calculated with our approach]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-julia.png}}
  \caption[]{A comparison of $F_{sss}$ function calculated using our approach
    with its precise values.}
  \label{fig:sss-verification}
\end{figure*}

To test $F_{ssv}$ and $F_{svv}$ we use the following relations for such a set
$A$ where all non-void phase is covered by a ball with radius $R$:
\begin{align}
  F^n_{ssv}(x_1, x_2) &= F^n_{ss}(x_1) \qquad x_2 > R \\
  F^n_{svv}(x_1, x_2) &= F^n_{sv}(x_1) \qquad x_2 > R
\end{align}
$F_{ss}$ and $F_{sv}$ functions are well-known for a ball of radius $R$ (solid
phase) placed in the center of cube of volume $V$ (void phase):
\begin{align}
  F_{ss}(r, R) &= \frac{1}{V} \left\{
    \begin{array}{ll}
      2\pi R^2/r & \quad r < 2R \\
      0 & \quad \text{otherwise}
    \end{array}
    \right.\\
  F_{sv}(r, R) &= \frac{1}{V} \left\{
    \begin{array}{ll}
      \pi Rr + 2\pi R^2 & \quad r < 2R \\
      4\pi R^2 & \quad \text{otherwise}
    \end{array}
    \right.
\end{align}
The comparison of our algorithm against theory is shown on
\cref{fig:surface-verification}. Radius of the ball is chosen to be $R=0.2$.
\begin{figure*}[tp]
  \centering
  \subfigure[$F_{ssv}$]{
    \includegraphics[width=0.45\linewidth]{images/ball-ssv.png}
    \label{fig:balls-ssv}}
  \hfill
  \subfigure[$F_{svv}$]{
    \includegraphics[width=0.45\linewidth]{images/ball-svv.png}
    \label{fig:ball-svv}}
  \caption[]{Comparison of $F_{ssv}$ and $F_{svv}$ functions for a ball with the
    radius $0.2$ with theoretical values.}
  \label{fig:surface-verification}
\end{figure*}

@@

\begin{table}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Limestone & XCT &  $600 \times 600 \times 600$ & 3.02 & 0.9712 \\
    Soil & XCT & $160 \times 160 \times 160$ & 2.25 & 0.9210 \\
    Shale & XCT & $160 \times 160 \times 160$ & 2.25 & 0.8912 \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table}

\begin{figure*}[tp]
  \centering
  \subfigure[Limestone]{
    \includegraphics[width=0.45\linewidth]{images/carb.png}
    \label{fig:sample-limestone}}
  \hfill
  \subfigure[Sandstone (different clusters of void phase are shown in color)]{
    \includegraphics[width=0.45\linewidth, frame]{images/sandstone1.png}
    \label{fig:sample-sandstone}}
  \vskip\baselineskip
  \subfigure[Soil]{
    \includegraphics[width=0.45\linewidth]{images/soil.png}
    \label{fig:sample-soil}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.45\linewidth]{images/shale.png}
    \label{fig:sample-shale}}
  \caption[]{Images of samples used for calculation of higher-order correlation
    functions.}
  \label{fig:samples}
\end{figure*}

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.45\linewidth]{images/carb.npy-surf3.png}
  \hfill
  \includegraphics[width=0.45\linewidth]{images/carb.npy-surf2void.png}
  \vskip\baselineskip
  \includegraphics[width=0.45\linewidth]{images/carb.npy-surfvoid2.png}
  \hfill
  \includegraphics[width=0.45\linewidth]{images/carb.npy-s3.png}
  \vskip\baselineskip
  \includegraphics[width=0.45\linewidth]{images/carb.npy-c3.png}
  \caption[]{Correlation functions for carbonate sample
    (\cref{fig:sample-limestone}).}
  \label{fig:sample-limestone-cf}
\end{figure}

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-surf2void.png}
  \hfill
  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-surfvoid2.png}
  \vskip\baselineskip
  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-s3.png}
  \hfill
  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-c3.png}
  \caption[]{Correlation functions for sandstone sample
    (\cref{fig:sample-sandstone}).}
  \label{fig:sample-sandstone-cf}
\end{figure}

\begin{figure*}[tp]
  \centering
  \subfigure[Shale]{
    \includegraphics[width=0.45\linewidth]{images/shale-s3.png}
    \label{fig:shale-s3}}
  \hfill
  \subfigure[Soil]{
    \includegraphics[width=0.45\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
    anisotropy more visible. It can be observed that the samples have
    cavities elongated along the vector $(1, 1, 0)$.}
  \label{fig:heatmaps}
\end{figure*}

@@

The main advantage of our algorithm is its parallelizability and ease of
implementation. An equivalent operation for rotation of test triangles is a
rotation of the whole input image which we have implemented in our
CorrelationFunctions.jl package. By applying a rotation to the input first we
made a rest of the algorithm cache-friendly by avoiding random memory access.
\begin{figure}[tp]
  \centering

  \subfigure[An original image of an anisotropic pore.]{
    \includegraphics[width=0.45\linewidth, frame]{images/aniso.png}
    \label{fig:aniso-unrot}}
  \hfill
  \subfigure[A rotated image of pore, so it is elongated along the axis $X$.]{
    \includegraphics[width=0.45\linewidth, frame]{images/aniso-rot.png}
    \label{fig:aniso-rot}}
  \vskip\baselineskip
  \subfigure[$S_3$ function for the original image]{
    \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}}
  \hfill
  \subfigure[$S_3$ function for the rotated image. A vector $(0.92, -0.4)$ is a
    direction of elongation of the pore.]{
  \includegraphics[width=0.3\linewidth]{images/aniso-rot-s3.png}}
  \hfill
  \subfigure[$S_3$ function averaged across 100 random rotations.]{
    \includegraphics[width=0.3\linewidth]{images/aniso-avg-s3.png}
    \label{fig:aniso-avg}}
  \caption[]{Behaviour of our algorithm for calculation of the $S_3$ function
    when dealing with highly anisotropic media. The pattern \cref{fig:pattern}
    which we use in our algorithm is most sensitive to anisotropy which is
    directed along one of the axes. A result on \cref{fig:aniso-avg} is similar
    to the algorithm proposed by Malmir~et~al.}
  \label{fig:aniso}
\end{figure}

>>>>

\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs]{revtex4-1}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage[export]{adjustbox}

@@

\begin{document}
\preprint{APS/123-QED}

\author{Vasily~Postnicov\textsuperscript{1}}
\author{Marina~V.~Karsanina\textsuperscript{1}}
\author{Aleksey~Khlyupin\textsuperscript{1,2}}
\author{Kirill~M.~Gerke\textsuperscript{1}}
\email{kg@ifz.ru}

\affiliation{\textsuperscript{1}Schmidt Institute of Physics of the Earth of
  Russian Academy of Sciences, Moscow, 107031, Russia}
\affiliation{\textsuperscript{2}Moscow Institute of Physics and Technology,
  Dolgoprudny, 141701, Russia}

@@

\keywords{Arrays, multiplication, addition}

@@

There are two common boundary conditions when applying $\mathfrak{S}$. The
first condition is to extend $A_n$ periodically (\cref{fig:s3-periodic}) when
accessing out-of-bounds array elements. In this case $\mathfrak{S}_z$ is a
circular shift operator:
\begin{equation}
  A[x] \leftarrow A[x+z \mod d]
\end{equation}
In this case $Norm(A, x_1, x_2)$ does not depend on $x_1$ and $x_2$ and
is equal to the total number of elements in $A$. The second condition is to
replace out-of-bound elements with zeros (so-called zero padding)
(\cref{fig:s3-zeros}). A formula for $Norm(A, x_1, x_2)$ in this case is in
\ref{sec:number-of-trials} and $\mathfrak{S}_z$ is defined as follows:
\begin{equation}
  A[x] \leftarrow \left\{
  \begin{array}{ll}
    A[x+z] & \quad \text{if $x+z$ is a correct index in $A$} \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation}
\begin{figure*}[tp]
  \centering
  \subfigure[Periodic boundary conditions]{
    \includegraphics[width=0.4\linewidth]{images/periodic.png}
    \label{fig:s3-periodic}}
  \hfill
  \subfigure[Zero padding]{
    \includegraphics[width=0.4\linewidth]{images/zeros.png}
    \label{fig:s3-zeros}}
  \caption[]{Computation of unnormalized $S_3$ function at point $(1, 2)$ for
    one-dimensional sequence of length 8.}
  \label{fig:s3-computation}
\end{figure*}

@@

On \cref{fig:balls} there is an intersection of such a set with $R = 0.02$ and
$\lambda=5000$ and a cube $[0, 1]^3$. Because $R \ll 1$, we can use
\cref{eq:s2-balls} to verify our computations -- this is exactly what we present on
\cref{fig:balls-s3-comparison}.
\begin{figure*}[tp]
  \centering
  \subfigure[Realization of overlapping balls]{
    \includegraphics[width=0.4\linewidth]{images/balls.png}
    \label{fig:balls}}
  \hfill
  \subfigure[A plot of $S_3(0, r)$ computed with our algorithm and theoretical
    formula.]{
    \includegraphics[width=0.4\linewidth]{images/balls-s3.png}
    \label{fig:balls-s3-comparison}}
  \caption[]{A comparison of calculated and theoretical values of $S_3$ function
    for overlapping balls.}
  \label{fig:s3-verification}
\end{figure*}

@@

The test is performed by firstly evaluating the inequation in a cube
$[-1, 1]^3$ and obtaining precise values of $F_{sss}$ and secondly computing
$F_{sss}$ with our algorithm, giving a discretized $400 \times 400 \times 400$
pixels wide image as the input. $F_{sss}$ function is evaluated in $XY$
plane. Pointwise relative error of $F_{sss}$ is on
\cref{fig:sss-dumbbell-error}. Maximal relative error in the area distanced
farther than 0.1 (20 pixels) from curves of discontinuity (see
\cref{fig:sss-dumbbell-precise}) is no more than 20\%.
\begin{figure*}[tp]
  \centering
  \subfigure[The dumbbell-like object used in testing of $F_{sss}$ computation]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell.png}
    \label{fig:sss-dumbbell}}
  \hfill
  \subfigure[Relative error of computation]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-err.png}
    \label{fig:sss-dumbbell-error}}
  \vskip\baselineskip
  \subfigure[$F_{sss}$: precise. The correlation function is undefined (has type
    II discontinuity) at curves A, B and C.]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-precise.png}
    \label{fig:sss-dumbbell-precise}}
  \hfill
  \subfigure[$F_{sss}$: calculated with our approach]{
    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-julia.png}}
  \caption[]{A comparison of $F_{sss}$ function calculated using our approach
    with its precise values.}
  \label{fig:sss-verification}
\end{figure*}

To test $F_{ssv}$ and $F_{svv}$ we use the following relations for such a set
$A$ where all non-void phase is covered by a ball with radius $R$:
\begin{align}
  F^n_{ssv}(x_1, x_2) &= F^n_{ss}(x_1) \qquad x_2 > R \\
  F^n_{svv}(x_1, x_2) &= F^n_{sv}(x_1) \qquad x_2 > R
\end{align}
$F_{ss}$ and $F_{sv}$ functions are well-known for a ball of radius $R$ (solid
phase) placed in the center of cube of volume $V$ (void phase):
\begin{align}
  F_{ss}(r, R) &= \frac{1}{V} \left\{
    \begin{array}{ll}
      2\pi R^2/r & \quad r < 2R \\
      0 & \quad \text{otherwise}
    \end{array}
    \right.\\
  F_{sv}(r, R) &= \frac{1}{V} \left\{
    \begin{array}{ll}
      \pi Rr + 2\pi R^2 & \quad r < 2R \\
      4\pi R^2 & \quad \text{otherwise}
    \end{array}
    \right.
\end{align}
The comparison of our algorithm against theory is shown on
\cref{fig:surface-verification}. Radius of the ball is chosen to be $R=0.2$.
\begin{figure*}[tp]
  \centering
  \subfigure[$F_{ssv}$]{
    \includegraphics[width=0.4\linewidth]{images/ball-ssv.png}
    \label{fig:balls-ssv}}
  \hfill
  \subfigure[$F_{svv}$]{
    \includegraphics[width=0.4\linewidth]{images/ball-svv.png}
    \label{fig:ball-svv}}
  \caption[]{Comparison of $F_{ssv}$ and $F_{svv}$ functions for a ball with the
    radius $0.2$ with theoretical values.}
  \label{fig:surface-verification}
\end{figure*}

@@

\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Limestone & XCT &  $600 \times 600 \times 600$ & 3.02 & 0.9712 \\
    Soil & XCT & $160 \times 160 \times 160$ & 2.25 & 0.9210 \\
    Shale & XCT & $160 \times 160 \times 160$ & 2.25 & 0.8912 \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table*}

\begin{figure*}[tp]
  \centering
  \subfigure[Limestone]{
    \includegraphics[width=0.4\linewidth]{images/carb.png}
    \label{fig:sample-limestone}}
  \hfill
  \subfigure[Sandstone (different clusters of void phase are shown in color)]{
    \includegraphics[width=0.4\linewidth, frame]{images/sandstone1.png}
    \label{fig:sample-sandstone}}
  \vskip\baselineskip
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil.png}
    \label{fig:sample-soil}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale.png}
    \label{fig:sample-shale}}
  \caption[]{Images of samples used for calculation of higher-order correlation
    functions.}
  \label{fig:samples}
\end{figure*}

\begin{figure*}[tp]
  \centering
  \includegraphics[width=0.4\linewidth]{images/carb.npy-surf3.png}
  \hfill
  \includegraphics[width=0.4\linewidth]{images/carb.npy-surf2void.png}
  \vskip\baselineskip
  \includegraphics[width=0.4\linewidth]{images/carb.npy-surfvoid2.png}
  \hfill
  \includegraphics[width=0.4\linewidth]{images/carb.npy-s3.png}
  \vskip\baselineskip
  \includegraphics[width=0.4\linewidth]{images/carb.npy-c3.png}
  \caption[]{Correlation functions for carbonate sample
    (\cref{fig:sample-limestone}).}
  \label{fig:sample-limestone-cf}
\end{figure*}

\begin{figure*}[tp]
  \centering
  \includegraphics[width=0.4\linewidth]{images/sandstone1.png-surf2void.png}
  \hfill
  \includegraphics[width=0.4\linewidth]{images/sandstone1.png-surfvoid2.png}
  \vskip\baselineskip
  \includegraphics[width=0.4\linewidth]{images/sandstone1.png-s3.png}
  \hfill
  \includegraphics[width=0.4\linewidth]{images/sandstone1.png-c3.png}
  \caption[]{Correlation functions for sandstone sample
    (\cref{fig:sample-sandstone}).}
  \label{fig:sample-sandstone-cf}
\end{figure*}

\begin{figure*}[tp]
  \centering
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale-s3.png}
    \label{fig:shale-s3}}
  \hfill
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
    anisotropy more visible. It can be observed that the samples have
    cavities elongated along the vector $(1, 1, 0)$.}
  \label{fig:heatmaps}
\end{figure*}

@@

The main advantage of our algorithm is its parallelizability and ease of
implementation. An equivalent operation for rotation of test triangles is a
rotation of the whole input image which we have implemented in our
CorrelationFunctions.jl package. By applying a rotation to the input first we
made a rest of the algorithm cache-friendly by avoiding random memory access.
\begin{figure*}[tp]
  \centering
  \subfigure[An original image of an anisotropic pore.]{
    \includegraphics[width=0.4\linewidth, frame]{images/aniso.png}
    \label{fig:aniso-unrot}}
  \hfill
  \subfigure[A rotated image of pore, so it is elongated along the axis $X$.]{
    \includegraphics[width=0.4\linewidth, frame]{images/aniso-rot.png}
    \label{fig:aniso-rot}}
  \vskip\baselineskip
  \subfigure[$S_3$ function for the original image]{
    \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}}
  \hfill
  \subfigure[$S_3$ function for the rotated image. A vector $(0.92, -0.4)$ is a
    direction of elongation of the pore.]{
  \includegraphics[width=0.3\linewidth]{images/aniso-rot-s3.png}}
  \hfill
  \subfigure[$S_3$ function averaged across 100 random rotations.]{
    \includegraphics[width=0.3\linewidth]{images/aniso-avg-s3.png}
    \label{fig:aniso-avg}}
  \caption[]{Behaviour of our algorithm for calculation of the $S_3$ function
    when dealing with highly anisotropic media. The pattern \cref{fig:pattern}
    which we use in our algorithm is most sensitive to anisotropy which is
    directed along one of the axes. A result on \cref{fig:aniso-avg} is similar
    to the algorithm proposed by Malmir~et~al.}
  \label{fig:aniso}
\end{figure*}
